---
title: Future Meeting Topic Interest
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)
library(kableExtra)
```


## AI Topic Interest

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height = 8.32, fig.width = 8.32}
df %>% select(InterestCustomAITool, CombinedInterestAIPolicy, CombinedInterestEthicalAI) %>%
    pivot_longer(everything(), values_to = "whichResponse", names_to = "whichAI") %>%
    mutate(whichResponse = recode(whichResponse, "yes" = "Yes", "Yes, definitely" = "Yes"),
           whichResponse = factor(whichResponse, levels = c("Not interested", "Maybe", "Yes")),
           whichTopic = case_when(whichAI == "InterestCustomAITool" ~ "Tools and infrastructure for building custom AI tools",
                                  whichAI == "CombinedInterestAIPolicy" ~ "Policy and regulation related to AI",
                                  whichAI == "CombinedInterestEthicalAI" ~ "Ethical usage and development of AI for scientific research")) %>%
    group_by(whichResponse, whichTopic) %>%
    summarize(n = n()) %>%
    drop_na() %>%
    ggplot(aes(x = n, y=whichResponse, fill=whichTopic)) +
    facet_wrap(~whichTopic, nrow=3) +
    geom_bar(stat = "identity") +
    theme_bw() +
    xlab("Response Count") +
    ylab("") +
    theme(legend.position = "none", text = element_text(size = 20)) +
    ggtitle("Would you be interested in\na talk/discussion about...")
```

## Respondent provided suggestions

```{r echo=FALSE, message=FALSE, warning=FALSE}
userSpecifiedTOI <- df %>% select(TopicsOfInterest) %>%
    mutate(TopicsOfInterest = recode(TopicsOfInterest, "Not sure" = NA_character_)) %>% #change Not sure to NA
    filter(!str_detect(TopicsOfInterest, "but")) %>% #remove not suggestions
    drop_na() %>% #drop the NA I introduced
    separate_longer_delim(TopicsOfInterest, delim = "; ") 

expanded <- rbind(
                  userSpecifiedTOI %>%
                    filter(!str_detect(TopicsOfInterest, ", ")), #already expanded because of separate_longer_delim with semicolon
                  userSpecifiedTOI %>%
                    filter(str_detect(TopicsOfInterest, ", ")) %>% 
                    mutate(TopicsOfInterest = str_replace_all(TopicsOfInterest, "e.g.", "eg"), #remove extra periods so I can split on period
                           TopicsOfInterest = str_replace_all(TopicsOfInterest, "eggement", "engagement")) %>% #fix spelling
                    separate_longer_delim(TopicsOfInterest, delim=". ") %>% #split on end of thought
                    separate_longer_delim(TopicsOfInterest, delim="?)") %>% #split on end of thought
                    mutate_at(.vars = "TopicsOfInterest", .funs = trimws) %>% #remove white space delimiters 
                    separate_longer_delim(TopicsOfInterest, delim=", ") %>% #split on commas within lists
                    mutate(TopicsOfInterest = 
                             recode(TopicsOfInterest, "Additionally" = NA_character_, #remove adverb
                                                      "especially as these tools become more prevalent" = NA_character_, #remove extraneous description
                                                      "I would also be interested in any discussions of AI-adjacent topics such as the ones mentioned below in the \"Would you be interested...\" question" = NA_character_)) %>% #not really a suggested/novel topic since already asked in survey
                    drop_na() %>% #drop the NAs I introduced
                    mutate(TopicsOfInterest = str_trim(TopicsOfInterest),
                      TopicsOfInterest = 
                             recode(TopicsOfInterest, "git tools and patterns for branching/committing releases." = "Open Source software development strategies - git tools and patterns for branching/committing releases.", #add the original descriptor back
                                                      "One idea is for another presentation on mentoring specifically undegaduates/trainees (I believe there might have been one in the past"= "mentoring specifically undergraduates/trainees", #simplify
                                                      "or about how scientific education in the computational science sphere might evolve with the increase in generative AI tools (eg how they may hinder or enhance training)" = "how the increase in generative AI tools may hinder or enhance computational science training", #simplify
                                                      "I think presentations on new \"trends\" in computational tools outside of AI might be useful: for instance" = "new trends in computational tools outside of AI", #simplify
                                                      "a presentation dedicated to Jupyter Notebook-based resources" = "Jupyter Notebook-based resources", #simplify
                                                      "or a presentation on how new technologies can improve existing tools (eg how Rust can be used to speed up tools likegeapy)" = "how new technologies can improve existing tools (eg how Rust can be used to speed up tools like gseapy)", #simplify
                                                      "or current \"hot topics\" (eg knowleg graphs" = "knowledge graphs", #simplify
                                                      "computer vision)" = "computer vision"),
                      TopicsOfInterest = na_if(TopicsOfInterest, "")) %>%
                    drop_na()
                  )

kableExtra::kable(expanded, table.attr = "style='width:20%;'")
```

## Interest in being a speaker/discussion leader

`r nrow(df %>% select(BeingGuestInterest) %>% mutate(BeingGuestInterest = recode(BeingGuestInterest, "No" = NA_character_)) %>% filter(!is.na(BeingGuestInterest)))` respondents expressed interest in being a speaker/discussion leader for future meetings. The topics that they suggested they could cover include 

```{r echo=FALSE, message=FALSE, warning=FALSE}
BeingGuest <- df %>% select(BeingGuestInterest) %>% 
       mutate(BeingGuestInterest = str_trim(BeingGuestInterest),
              BeingGuestInterest = recode(BeingGuestInterest, "No" = NA_character_, "I might be interested in presenting on software quality, and general software development practices topics." = "Software quality and general software development practices", "I would be happy to discuss data provenance and bioinformatic data reproducibility" = "Data provenance and bioinformatic data reproducibility", "Yes, guest discussion leader. I would like to talk about tools and platforms to encourage user engagement, develop tutorials and FAIR content development for long term usage (https://elixir-europe-training.github.io/ELIXIR-TrP-FAIR-training-handbook/)" = "Tools and platforms to encourage user engagement, develop tutorials and FAIR content development for long term usage")) %>%
       filter(!is.na(BeingGuestInterest))

kableExtra::kable(BeingGuest, table.attr = "style='width:20%;'")
```

## Speaker/Discussion leader recommendations

> Do you have recommendations of other speakers/discussion leaders you think would be great for an OPEN meeting? 

```{r echo=FALSE, message=FALSE, warning=FALSE}
speakerRec <- df %>% mutate(SpeakerRecs = recode(SpeakerRecs, "No" = NA_character_)) %>% select(SpeakerRecs) %>% drop_na()

kableExtra::kable(speakerRec, table.attr = "style='width:20%;'")
```

["Dr. Kawamoto directs the University’s ReImagine EHR initiative, which is a multi-stakeholder enterprise initiative for improving health and health care through interoperable electronic health record (EHR) innovations"](https://medicine.utah.edu/faculty/kensaku-kawamoto)

## Preferred Meeting Styles

Note: Each respondent could select multiple meeting styles

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 14.98, fig.height = 7.38}
mycolors <- c(
  "Discussion" = "#F8766D",
  "Guest Education Session" = "#B79F00",
  "ITN Education Session" = "#00BA38",
  "Research Activity" = "#00BFC4",
  "Research Talk" = "#619CFF",
  "Software Introduction" = "#F564E3"
)

df %>%
    select(Timestamp, StylePref) %>%
    separate_longer_delim(StylePref, delim = ", ") %>%
    mutate(n_responses = length(unique(Timestamp))) %>%
    group_by(StylePref, n_responses) %>%
    summarize(n = n()) %>%
    mutate(percentage = n/n_responses*100) %>%
    arrange(-n) %>%
    select(StylePref, percentage) %>%
    mutate(MeetingAnnot = case_when(StylePref == "Guest speaker talks about a course or training resource" ~ "Guest Education Session",
       StylePref == "Guest speaker about a topic" ~ "Guest Education Session",
       StylePref == "Multiple guest speakers about a topic" ~ "Guest Education Session",
                                    StylePref == "Discussions about a topic" ~ "Discussion",
                                    StylePref == "Co-working on a project like a manuscript" ~ "Research Activity",
                                    StylePref == "Guest speaker about their research" ~ "Research Talk",
                                    StylePref == "A new style where we get CliffNote presentations on books of interest" ~ "ITN Education Session",
                                    StylePref == "A recorded forum for a podcast episode where cancer informatics topics are discussed" ~ "Discussion"),
       MeetingAnnot = factor(MeetingAnnot, levels = c("Discussion", "Guest Education Session", "ITN Education Session", "Research Activity", "Research Talk", "Software Introduction")),
       StylePref = recode(StylePref, "A new style where we get CliffNote presentations on books of interest" = "A new style: CliffNote presentations\non books of interest", "A recorded forum for a podcast episode where cancer informatics topics are discussed" = "A recorded forum for a podcast episode\nwhere cancer informatics topics are discussed", "Guest speaker talks about a course or training resource" = "Guest speaker talks about\na course or training resource")) %>%
    ggplot(aes(x = percentage, y = reorder(StylePref, percentage), fill=MeetingAnnot)) +
    geom_bar(stat="identity") +
    xlim(0,100) +
    xlab("Percentage of responses") +
    ylab("") +
    theme_bw() +
    theme(text = element_text(size = 20)) +
    scale_fill_manual(values=mycolors)+
    labs(fill=NULL) +
    ggtitle("What style of meeting do you prefer?")
```